### 2014-12-08 Draft/evaluation.tex
updated based on Dr. Xie's Comments

We used the API documents of the following two libraries as subjects for our evaluation. 
\begin{itemize}
	\item \amazonAPI\: provides a REST based web services interface to store and retrieve data on the web.
	Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, and inexpensive infrastructure. 
	\CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.

@@

	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by a programming language.
\end{itemize}
We chose \CodeIn{Amazon S3}, \CodeIn(PayPal) and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
First two authors manually labeled each sentence in the Java API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
Based on the discussions first author annotated the rest of the subject APIs. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.

@@

We then use these measures to identify relative effectiveness of \tool by executing multiple classifiers on the annotated sentences.
We tested the classifiers using a stratified n-fold cross-validation approach,
using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}
The cross validation ensures that every sentence is used for training and testing,
thus producing low bias and variance.
In particular, we execute the classifiers in two different configurations.
First we execute the classifiers using the words in the sentnces as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
We next execute the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$). 
Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are are indicative of effectiveness of the constraint statements inferred using \tool.

@@

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
1	& AdaBoost	& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol2	& NaiveBayes	& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol4	& Decision Tree	& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
5	& Winnow	& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol6	& MaxEnt	& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
	& Total	& 0.59	& 0.62	& 0.55	& 0.77	& 0.6	& 0.65	& 0.19	& -0.02	& 0.1	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\end{center}
\end{table*}

@@

\begin{tabular}{lccccc}
\topline
\headcol 	API 		& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 	& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 					& \\ 
\rowcol 	Total 		& 746 	& 4060 	& 90		& 63 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

@@

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
Column ``Trainer'' lists the names of the classifiers used to train the model for classifications in \tool.
Columns P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained without the features proposed by \tool.
Columns P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained with the features proposed by \tool.
Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in\CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.

For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, and Max Entropy. We used Na{\"i}ve Bayes as the weaker classifier with AdaBoost. We used \CodeIn{Mallet}~\cite{mallet} implementation of these classifiers for our experiments.

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 77.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 19\%, without significant reduction in the recall (average 2\%).

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
%For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
%\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
%However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
%\tool, thus incorrectly identifies the sentence as a constraint sentence.   
%
%
%Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
%and/or inadequacy of generic dictionaries for synonym analysis.
%For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
%from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
%The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
%However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
%This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
%because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
%We observed 8 instances of previously described example in our results.
%
%If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
%our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
%Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
%In the future, we plan to investigate techniques to construct better domain dictionaries for software API. 
%
%We next present an example to illustrate how \tool\ fails identify a constraint sentence (producing false negative).
%False negatives are undesirable in the context of our problem domain
%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
%For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
%from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
%The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
%before calling the current method.
%However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
%In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints. 
%
%Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
%For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
%those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
%The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
%However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
%which eventually results into incorrect classification. 
%
%Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
%Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
%used in current prototype implementation will further improve the precision and recall of \tool.

@@

Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives). Overall, accuracy of \tool\ can be significantly improved by lowering the false negative rate in identifying the constraint sentences.

@@

In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\% respectively. Furthermore, we also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%. Furthermore, also provide discussion that a false positives rate and false negatives rate can be further improved by improving the underlying NLP infrastructure. Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of two different API's: JDK \CodeIn{java.io} and \amazon. On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazon\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Furthermore, the difference in the functionalities provided by the two API's also address the issue of over fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.

Threats to internal validity include the correctness of our prototype implementation in extracting temporal constraints and labeling a statement as a constraint statement. To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation. Furthermore, we ensured that the results were individually verified and agreed upon by two authors, using the \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure the inter-rater agreement.

>>>>

We used the API documents of the following three libraries as subjects for our evaluation. 
\begin{itemize}
	\item \amazonAPI\: provides a REST based web services interface to store and retrieve data on the web.
	Furthermore, \CodeIn{Amazon S3} also empowers a developer with rich set of API methods to access a highly scalable, reliable, secure, fast, and inexpensive infrastructure. 
	\CodeIn{Amazon S3} is reported to store more than 2 trillion objects as of April 2013 and gets over 1.1 million requests per second at peak time~\cite{amazons3stats}.

@@

	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by any programming language.
\end{itemize}
We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
First two authors manually labeled each sentence in the Java API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently.
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.
Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.

@@

We then use these measures to identify relative effectiveness of \tool\ by executing multiple classifiers on the annotated sentences.
We tested the classifiers using a stratified n-fold cross-validation approach,
using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}.
The cross validation ensures that every sentence is used for training and testing,
thus producing low bias and variance.
In particular, we execute the classifiers in two different configurations.
First we executed the classifiers using the words in the sentences as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
We next executed the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$). 
Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by \tool\ approach.

@@

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
			1	& AdaBoost			& 0.52	& 0.81	& 0.61	& 0.7	& 0.78	& 0.74	& 0.18	& -0.03	& 0.13	\\
\rowcol		2	& NaiveBayes		& 0.49	& 0.67	& 0.56	& 0.74	& 0.65	& 0.69	& 0.25	& -0.02	& 0.13	\\
			3	& Balanced Winnow	& 0.77	& 0.76	& 0.76	& 0.78	& 0.77	& 0.77	& 0.01	& 0.01	& 0.01	\\
\rowcol		4	& Decision Tree		& 0.82	& 0.58	& 0.66	& 0.92	& 0.41	& 0.56	& 0.1	& -0.17	& -0.1	\\
			5	& Winnow			& 0.19	& 0.41	& 0.15	& 0.8	& 0.51	& 0.59	& 0.61	& 0.1	& 0.44	\\
\rowcol		6	& MaxEnt			& 0.69	& 0.48	& 0.55	& 0.76	& 0.46	& 0.56	& 0.07	& -0.02	& 0.01	\\
			7	& c45				& 0.78	& 0.4	& 0.52	& 0.82	& 0.59	& 0.67	& 0.04	& 0.19	& 0.15	\\
\midline
			& Average			& 0.61	& 0.59	& 0.54	& 0.79	& 0.6	& 0.65	& 0.18	& 0.01	& 0.11	\\
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:resultsRQ1}
\end{center}
\end{table*}

@@

\begin{tabular}{lccccc}
\topline
\headcol 	API 			& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 		& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 14				& 70.0\\ 
\rowcol 	Total 			& 746 	& 4060 	& 110		& 77 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}

@@

In this section, we quantify the effectiveness of \tool\ in identifying constraint sentences by answering RQ1.
Table~\ref{tab:resultsRQ1} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences using various classifiers.
Column ``Trainer'' lists the names of the classifiers used to train the model for classifications in \tool.
Columns P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained without the features proposed by \tool.
Columns P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$ list the \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of classifiers trained with the features proposed by \tool.
Finally, columns P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ list the improvement factors in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively.

For our evaluation we used following well known classifiers: AdaBoost (or adaptive boosting), Na{\"i}ve Bayes, Winnow, Balanced Winnow, Decision Tree, Max Entropy, and c45. We used Na{\"i}ve Bayes as the weaker classifier with AdaBoost. We used \CodeIn{Mallet}~\cite{mallet} implementation of these classifiers for our experiments.

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precisoin} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%. There is also a slight increase in the recall (average 1\% gain).

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence. \textbf{A example goes here}
%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a constraint sentence (producing false positives).
%For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class.
%\tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''.
%However \tool\ fails to make the distinction that it happens internally (enforced in the body) in the method.
%\tool, thus incorrectly identifies the sentence as a constraint sentence.   
%
%
%Another major source of FPs is the incorrect parsing of sentences by the underlying NLP infrastructure
%and/or inadequacy of generic dictionaries for synonym analysis.
%For instance, consider the sentence ``\textit{If this stream has an associated channel then the channel is closed as well.}''
%from the \CodeIn{close} method description from \CodeIn{FileOutputStream}.
%The sentence describes an effect that happens as a result of calling the \CodeIn{close} method and does not describe any temporal constraint.
%However, \tool\ annotates the sentence as a constraint sentence because underlying Wordnet dictionaries matches the word ``has'' as a synonym of ``get''.
%This incorrect matching in turn causes \tool\ to incorrectly annotate the sentence as constraint sentence
%because ``has'' is matched against \CodeIn(get) method in \CodeIn{FileOutputStream}.
%We observed 8 instances of previously described example in our results.
%
%If we manually fixed the Wordnet dictionaries to not match ``has'' and ``get'' as synonyms,
%our precision is further increased to 70.8\% effectively increasing the F-Score of \tool\ to 71.2\%.
%Although an easy fix, we refrained from including such modifications for reporting the results to stay true to our approach.
%In the future, we plan to investigate techniques to construct better domain dictionaries for software API. 
%

%
%Another major source of false negatives (similar to reasons for false positives) is the incorrect parsing of sentences by the underlying NLP infrastructure.
%For instance, consider the sentence ``\textit{If any in-memory buffering is being done by the application (for example, by a BufferedOutputStream object),
%those buffers must be flushed into the FileDescriptor (for example, by invoking OutputStream.flush) before that data will be affected by sync.}''
%The sentence describes that the \CodeIn{OutputStream.flush()} must be invoked before invoking the current method if in-memory buffering is performed.
%However, the length and complexity in terms of number of clauses causes the underlying Stanford parser to inaccurately annotate the dependencies,
%which eventually results into incorrect classification. 
%
%Overall, a significant number of false positives and false negatives will be reduced as the current NLP research advances the underlying NLP infrastructure.
%Furthermore, use of domain specific dictionaries as opposed to generic dictionaries
%used in current prototype implementation will further improve the precision and recall of \tool.

@@

We next present an example to illustrate how \tool\ fails infer constraints from a constraint sentence.
%False negatives are undesirable in the context of our problem domain
%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
before calling the current method.
However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.

%Another, major cause of failure for \tool\ in inferring temporal constraints from sentences is the failure to identify the sentence as a constraint sentences at the first place (false negatives). Overall, accuracy of \tool\ can be significantly improved by lowering the false negative rate in identifying the constraint sentences.

@@

In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 3900 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively. We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%. Furthermore, also provide discussion on why \tool\ does not or incorrectly infers temporal constraints. Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.

\subsection{Threats to Validity}
\label{sub:threats_to_validity}
Threats to external validity primarily include the degree to which the subject documents used in our evaluation are representative of true practice. To minimize the threat, we used API documents of three different API's: JDK \CodeIn{java.io}, \amazonAPI, \paypalAPI. On one hand, Java is a widely used programming language and \CodeIn{java.io} and is one of the main packages. In contrast, \amazonAPI\ provides HTTP based access to online storage allowing developers the freedom to write clients applications in any programming language. Finally, \paypalAPI\ provides a REST support for online financial transactions. The difference in the functionalities provided by the three API's also address the issue of over-fitting our approach to a particular type of API. The threat can be further reduced by evaluating our approach on more subjects API's.

Threats to internal validity include the correctness of our prototype implementation in extracting temporal constraints and labeling a statement as a constraint statement. To reduce the threat, we manually inspected all the constraints inferred against the API method descriptions in our evaluation. Furthermore, we ensured that the results were individually verified and agreed upon by two authors independently.

### 2014-12-08 Draft/example.tex
updated based on Dr. Xie's Comments

We next present a real world example to motivate our approach.
Through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this phenomena is that the documentation is often verbose and the information is distributed across various pages.
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
Often developers may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazon, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
Customer dissatisfaction caused by such issues with the delete bucket functionality, can lead to a loss in revenue.

The presented issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
In next section, we briefly discuss the related work pertinent to our approach.

>>>>

We next present a real world example to motivate our approach.
Through the example, we demonstrate that developers often ignore the temporal constraints of an API described in the documentation.
We suspect the reason for this behavior is that the documentation is often verbose and the information is distributed across various pages.
%For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.
Often developers may not have time (and/or patience) to go through all the documentation and may overlook some temporal constraints of the API,
resulting in defective client applications that invoke API methods in sequences prohibited by documentation.

@@

Consider the question asked in \textit{Stack Overflow}~\footnote{{\small \url{http://stackoverflow.com/questions/27267/delete-amazon-s3-buckets}}} as shown in Figure~\ref{fig:Stackoverflow}.
Stack Overflow is an online question and answer forum for professional and enthusiast programmers.
The query is about the delete functionality of a third-party software \CodeIn{S3Fox} to interact with \amazonAPI.
The inquisitor complains about an issue in the delete bucket functionality of the \CodeIn{S3Fox}.
The \CodeIn{S3Fox} developers overlooked the constraints in \amazonAPI\ developer documents, causing the issue.
The API document pertaining to the  delete bucket functionality states that before deleting the bucket, the objects in the buckets must be deleted.
\textit{``All objects (including all objects versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted''}.
Although the issue was fixed, one of the forum responses recommended the inquisitor to switch to another product.
Customer dissatisfaction caused by such issues with the delete bucket functionality can lead to a loss in revenue.

The presented issue can be easily detected using formal analysis tools.
For instance, a specification rule (temporal constraint) can be added to a static checker to verify
the presence of a call to delete object functionality before the call to delete bucket functionality.
%However, existing formal analysis accept only formal specifications but not informal constraints described in natural language.
%Thus, there is need for an approach to automatically translate the constraints described in natural language into a more formal notation.
We next briefly discuss the related work pertinent to our approach.
